---
title: "First Attempt at PowerPoint"
author: "Barry DeCicco"
date: "5/13/2020"
output: powerpoint_presentation
---

```{r setup,  collapse=TRUE, echo=FALSE}  

# load libraries as needed:
# 





library(psych)
library(tidyverse)
library(readr)

library(pastecs)
# https://stats.idre.ucla.edu/r/faq/how-can-i-get-a-table-of-basic-descriptive-statistics-for-my-variables/
# library(devtools)
# devtools::install_github("alastairrushworth/inspectdf")

library(inspectdf)   
# https://www.r-bloggers.com/part-2-simple-eda-in-r-with-inspectdf/

library(summarytools)
library(Hmisc)
library(inspectdf)
library(janitor)
library(htmlTable) 
library(kableExtra)


```

```{r setup_not_used, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

