---
title: "Introduction to RMarkdown"
author: "Barry DeCicco"
date: "5/13/2020"
output: powerpoint_presentation
params:
  year: 2018
  start_date: "2022-01-01"
  end_date:   "2022-21_31"
  region: Europe
  data_file: file.csv

---

```{r setup,  collapse=TRUE, echo=FALSE, include=FALSE}  

# load libraries as needed:

library(psych)
library(tidyverse)
library(readr)

library(pastecs)
# https://stats.idre.ucla.edu/r/faq/how-can-i-get-a-table-of-basic-descriptive-statistics-for-my-variables/
# library(devtools)
# devtools::install_github("alastairrushworth/inspectdf")

library(inspectdf)   
# https://www.r-bloggers.com/part-2-simple-eda-in-r-with-inspectdf/

library(summarytools)
library(Hmisc)
library(inspectdf)
library(janitor)
library(htmlTable) 
library(kableExtra)


```

```{r setup_not_used, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)


```


## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Chunk Options
(from: https://bookdown.org/yihui/rmarkdown-cookbook/chunk-options.html)

- **echo=FALSE**     This will prevent the code from being displayed.  
- **message=FALSE**  This will prevent messages from being displayed.
- **warning=FALSE**  This will prevent warnings from being displayed.
- **include=FALSE**  This will prevent **everything** from being displayed.
- **eval=FALSE**     This will prevent the chunk from being run.


## Slide with R Output

```{r cars, echo = TRUE}

summary(cars)
```

## Slide with Plot

```{r pressure, echo = TRUE }
plot(pressure)
```

