---
title: "Introduction to RMarkdown"
subtitle: "For ABS Network Lunch and Learn" 
author: "Barry DeCicco"
date: "5/13/2020"
output: 
  html_document:
  toc: true 
  toc_depth: 4 
  number_sections: true 
  toc_float: true 
params:
  year: 2018
  start_date: "2022-01-01"
  end_date:   "2022-21_31"
  region: Europe
  data_file: file.csv

---

```{r setup,  collapse=TRUE, echo=FALSE, include=FALSE}  

# load libraries as needed:

library(psych)
library(tidyverse)
library(readr)

library(pastecs)
# https://stats.idre.ucla.edu/r/faq/how-can-i-get-a-table-of-basic-descriptive-statistics-for-my-variables/
# library(devtools)
# devtools::install_github("alastairrushworth/inspectdf")

library(inspectdf)   
# https://www.r-bloggers.com/part-2-simple-eda-in-r-with-inspectdf/

library(summarytools)
library(Hmisc)
library(inspectdf)
library(janitor)
library(htmlTable) 
library(kableExtra)


```

```{r setup_not_used, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)


```


## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents.  When moving between different outputs, you might need to change the document.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

An R Markdown document consist of a header, text and code chunks.
R will run the code in the code chunks and render the results, mixing 
the output with the text.


## Languages

Blocks of code usually start with "``` {r chunkname, options}" and end with
"```".  The 'r' in the name tells R Markdown to use r to run the chunk.
"``` {python chunkname, options}" would cause the chunk to be run in python.

- There are at least 50 languages available.
- You will have to set up the language(s) in the options.
- These chunks will likely start and end in an independent run of the language; 
you will have to import and export results.


## Chunk Options

- **echo=FALSE**     This will prevent the code from being displayed.
- **message=FALSE**  This will prevent messages from being displayed.
- **warning=FALSE**  This will prevent warnings from being displayed.
- **include=FALSE**  This will prevent **everything** from being displayed.
- **eval=FALSE**     This will prevent the chunk from being run.

## Inline code

The results of any 'r' chunk are available in both the following chunks or
in the text.  Some things can be computed more automatically:
"format(Sys.time(), '%d %B, %Y')" started in: back-tick, r  and ended with
a back-tick, will cause R Markdown to process it as r code:
`r format(Sys.time(), '%d %B, %Y')`

## Parameters and calling other files

R Markdown can use parameters within and between documents.
For example, putting this into the header will cause a list, 'Params' to 
be created with the following names and values:

params:<p>
  year: 2018<p>
  start_date: "2022-01-01"<p>
  end_date:   "2022-21_31"<p>
  region: Europe<p>
  data_file: file.csv<p>

### Parameters and calling other files

One R Markdown file can call another, passing on parameters either
implicitly (using the default parameters in the header) or expliclitly,
passing a newly-specified list of parameters.

The called file can be called either as a fresh session, inheriting only
the parameters passed, or in a continuation of the existing session,
inheriting the full environment.


## Table of Contents, Code Folding

The following commands in the head will:

Display a table of contents (TOC)<p>
The TOC floats on the current page as you page down<p>
The TOC has 4 layers of depth (e.g., section 4, 4.1, 4.1.1, ...)<p>
The code is hidden by default, with a button to display it<p>

## Code for TOC and Code Folding

output:<p>
   html_document:<p>
        toc: true # table of contents true<p>
        toc_depth: 4 # up to four depths of headings<p>
        number_sections: true  #number sections at each table header<p>
        toc_float:  true  #to see table of contents on side\<p>
        code_folding: hide<p>

## Slide with R Output

```{r cars, echo = TRUE}

summary(cars)
```

## Slide with Plot

```{r pressure, echo = TRUE }
plot(pressure)
```

## References:

- Rstudio's reference:  https://rmarkdown.rstudio.com/
- 'R Markdown: The Definitive Guide': https://bookdown.org/yihui/rmarkdown/
- 'R Markdown Cookbook': https://bookdown.org/yihui/rmarkdown-cookbook/



